---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# estimtf

<!-- badges: start -->
<!-- badges: end -->

The `estimtf` provides functions to find the Maximum Likelihood estimates of parameters from parametric distributions and linear regression models using TensorFlow optimizers.

## Installation

You can install `estimtf` from GitHub with the following command:

``` r
install.packages('devtools')
devtools::install_github('SaraGarcesCespedes/estimtf', force=TRUE) 
```

## Example

This is a basic example that shows how to estimate the mean and standard deviation parameters from the normal distribution using the `mle_tf` function:

```{r example}
library(estimtf)

## Estimation of both normal distrubution parameters
x <- rnorm(n = 1000, mean = 10, sd = 3)

estimation <- mle_tf(x, 
                     xdist = "Normal", 
                     optimizer = "AdamOptimizer",
                     initpara = list(mean = 0.5, sd = 0.5),
                     hyperparameters = list(learning_rate = 0.1))
summary(estimation)
```

