---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

```{r echo=FALSE, results="hide", message=FALSE}
library(badger)
library(badgecreatr)
```


<!-- badges: start -->
[![R-CMD-check](https://github.com/SaraGarcesCespedes/estimtf/workflows/R-CMD-check/badge.svg)](https://github.com/SaraGarcesCespedes/estimtf/actions)
[![Licence](https://img.shields.io/badge/licence-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
![GitHub R package version](https://img.shields.io/github/r-package/v/SaraGarcesCespedes/estimtf)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/estimtf)](https://cran.r-project.org/package=estimtf)
<!-- [![Travis build status](https://travis-ci.com/SaraGarcesCespedes/estimtf.svg?branch=master)](https://travis-ci.com/SaraGarcesCespedes/estimtf) -->
<!-- badges: end -->

# estimtf

The `estimtf` package provides functions to find the Maximum Likelihood Estimates of parameters from probability distributions and linear regression models using the TensorFlow optimizers.

## Installation

You can install `estimtf` from GitHub with the following command:

``` r
install.packages('devtools')
devtools::install_github('SaraGarcesCespedes/estimtf', force=TRUE) 
```

## Example

This is a basic example that shows how to estimate the mean and standard deviation parameters from the normal distribution using the `mle_tf` function:

```{r example}
# Load the estimtf package
library(estimtf)

# Estimation of parameters mean and sd from the normal distribution

# Generate a sample from the normal distribution
x <- rnorm(n = 1000, mean = 10, sd = 3)

# Find the MLE of the parameters using the mle_tf function
estimation <- mle_tf(x, 
                     xdist = "Normal", 
                     optimizer = "AdamOptimizer",
                     initparam = list(mean = 0.5, sd = 0.5),
                     hyperparameters = list(learning_rate = 0.1))

# Get the summary of the estimates
summary(estimation)

```

