---
title: "Introduction to estimtf"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction_to_estimtf}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


The estimtf package provides functions to find the Maximum Likelihood estimates of parameters from parametric distributions and linear regression models using TensorFlow optimizers.

This document introduces you to estimtf’s set of tools, and shows you how to apply them to estimate these parameters.

## Load estimtf package from GitHub
```{r, eval=FALSE}
devtools::install_github('SaraGarcesCespedes/estimtf', force=TRUE)
library(estimtf)
```

## dist_estimtf2 function

This function is used to compute the Maximum Likelihood Estimators of distributional parameters using TensorFlow. Use `?dist_estimtf` for more details.

```{r, eval=FALSE}
# Estimation of both normal distrubution parameters
x <- rnorm(n = 1000, mean = 10, sd = 3)
estimation1<-dist_estimtf2(x, xdist = "Normal", 
                           optimizer = "AdamOptimizer", 
                           hyperparameters=list(learning_rate=0.1))

summary(estimation1)

# Estimation of parameter lambda from Instantaneous Failures distribution
pdf <- function(X, lambda) { 
(1/((lambda^2)*(lambda-1)))*              (lambda^2+X-2*lambda)*exp(-X/lambda)
}

x <-  c(3.4,0.0,0.0,15.8,232.8,8.8,123.2,47,154,103.2,89.8, 12.2)

estimation2<-dist_estimtf2(x = x, xdist = pdf, 
                          initparam =list(lambda=rnorm(1,2,1)),
                          optimizer = "AdamOptimizer",
                          hyperparameters=list(learning_rate=0.1), 
                          maxiter = 10000)
summary(estimation2)

```

As the `dist_estimtf` uses the TensorFlow distributions, the `mean` parameter from the Normal distribution is known as `loc` and the `sd` parameter is known as `scale`. 


## reg_estimtf function

This function is used to compute the Maximum Likelihood Estimators of regression parameters using TensorFlow. Use `?reg_estimtf` for more details.

```{r, eval=FALSE}
# Estimation of parameters of a Poisson regression model
counts <- c(18,17,15,20,10,20,25,13,12)
outcome <- gl(3,1,9)
treatment <- gl(3,3)
data <- data.frame(treatment, outcome, counts)
formulas <- list(rate.fo = ~ outcome + treatment)

estimation1 <-reg_estimtf(ydist =  counts ~ Poisson, 
                         formulas = formulas, data = data,
                         initparam = list(rate = 1.0), 
                         optimizer = "AdamOptimizer",
                         link_function = list(rate = "log"),
                         hyperparameters=list(learning_rate=0.1))

summary(estimation1)

# Estimation of parameters of a linear regression model with one fixed parameter
x <- runif(n = 1000, -3, 3)
y <- rnorm(n = 1000, mean = 5 - 2 * x, sd = 3)
data <- data.frame(y = y, x = x)
formulas <- list(loc.fo = ~ x)
initparam <- list(loc = list(Intercept = 1.0, x = 0.0))

estimation2<-reg_estimtf(ydist = y ~ Normal, formulas = formulas,
                         data = data,
                         fixparam = list(scale = 3), 
                         initparam = initparam,
                         optimizer = "AdamOptimizer",
                         hyperparameters=list(learning_rate= 0.1))

summary(estimation2)
```

As the `reg_estimtf` uses the TensorFlow distributions, the `lambda` parameter from the Poisson distribution is known as `rate`.


## estimglm function

This function is used to fit Generalized Linear Models using TensorFlow. Use `?estimglm` for more details.

```{r, eval=FALSE}
# Estimation of parameters from a simple linear regression model
data <- data.frame(dist = cars$dist, speed = cars$speed)
formula <- dist ~ speed
estimation <- estimglm(formula, family = "Normal", 
                       link_function =  "identity",
                       data = data, initcoeff = list(speed = 1),
                       optimizer = "AdamOptimizer",
                       hyperparameters = list(learning_rate=0.1),
                       maxiter = 10000)

summary(estimation)
predict(estimation, newdata = data.frame(speed = c(10, 40, 50)))
```

